Supplement 1: Different Response Distributions

### 2018-10-01 pkg/disttree/inst/draft/supplement/supplement_distributions.Rnw
added information on learning and testing data
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2303 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 2b8fc790aec696d98018ff8a7425bdf5a51be78d

To assess how appropriate the distributional assumption (left-censored Gaussian distribution
with censoring point zerol; or zero-censored for short) is, two questions are considered:
(1)~Are the tails of the distribution captured appropriately by a Gaussian distribution or
are \emph{heavier tails} required?
(2)~Is the point mass at zero (= no rain) driven by the same determinants as the
positive observations (= rain) or should this be captured by a \emph{separate parameter}?
For (1) we compare the zero-censored Gaussian with a \emph{zero-censored logistic} distribution and
for (2) a Gaussian \emph{hurdle model} (or two-part model with binary and zero-truncated parts)
is employed instead of the zero-censored Gaussian.

Just as in the main manuscript the performance of the distributional forest is also
compared with other commonly-used distributional regression models using the same
data set. Table~2 of the manuscript provides
an overview of all models considered and their specifications. As a reminder
the approaches are briefly summarized below.
%
\begin{itemize}

>>>>

To assess how appropriate the distributional assumption (left-censored Gaussian distribution
with censoring point zero; or zero-censored for short) is, two questions are considered:
(1)~Are the tails of the distribution captured appropriately by a Gaussian distribution or
are \emph{heavier tails} required?
(2)~Is the point mass at zero (= no rain) driven by the same determinants as the
positive observations (= rain) or should this be captured by a \emph{separate parameter}?
For (1) we compare the zero-censored Gaussian with a \emph{zero-censored logistic} distribution and
for (2) a Gaussian \emph{hurdle model} (or two-part model with binary and zero-truncated parts)
is employed instead of the zero-censored Gaussian.

Just as in the main manuscript the performance of the distributional forest is also
compared with other commonly-used distributional regression models using the same
data set. The models are learned on data from the first 24 years (1985--2008) and 
evaluated on the following 4 years (2009--2012). Table~2 of the manuscript provides 
an overview of all models considered and their specifications. As a reminder the 
approaches are briefly summarized below.
%
\begin{itemize}
